Combinatorics of the geometry of Wilson loop diagrams

### 2019-02-07 General WLD combinatorics.tex
inside/outside definition version 2.1

Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $P$ partions $n$ into two sets, $\{V_{in}(p), V_{out}(p)\}$, where $V_{in}(p)$ and $V_{out}(p)$ correspond to the two  cyclic subintervals of $[n]$ that lie on either side of $p$. This in turn defines three sets of propagators, $\{\cP_{in}, p, \cP_{out}\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas If $W$ has no propagators crossing $p$ and no other propagator supported on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$. The set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side. In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.

It remains to determine with set of propagators/vertices are refered to as on the inside of $p$ and which are on the outside. To do this, we impose a direction on $p$.

 \sanote{can we use the notation directed propagator here? to emphasize the notational change?}

@@

We may associate the propagators on the inside and outside of $p$ accordingly.

Note that under this definiton, $V_{in}(p, <_i) = V_{out}(p, <_j)$. That is, which set of propagators lie inside and outside of $p$ switch depending on the direction imposed $p$.

>>>>

Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $p$ partions $[n]$ into two cyclic subintervals of $[n]$, $\{[i+1, j], [j+1, i]\}$ that lie on either side of $p$. In the sequel we refer to these intervals as an interval inside and outside of $p$, depending on a ordering we associate to the propagator.

@@

Similarly, we may associate the ordering $<_j$ to $p$, in which case $V_{in}(p, <_i) = V_{out}(p, <_j)$ and $V_{out}(p, <_i) = V_{in}(p, <_j)$.

This in turn defines two sets of propagators, $\{\cP_{in}, \cP_{out}\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas The set $\cP_{in}$ (resp. $\cP_{out}$) is the set of propagators, not equal to $p$ \hlfix{whose support contains points in $V_{in}(p, <_*)$ (resp. $V_{in}(p, <_*)$), where $<_*$ refers to the appropriate ordering.}{Note, this means that paralell propagators are both on the inside and outside of $p$. Is that okay?} If $W$ has no propagators crossing $p$ and no other propagator supported entirely on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$. Under these circumstances, the set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side. In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.

As with the vertex sets,  which set of propagators lie inside and outside of $p$ switch depending on the direction imposed $p$.
